Physical Component Score and QALYs

### 2024-04-23 minos/testing/PCS_QALYs.Rmd
Additions to the PCS QALY notebook for sharing around SIPHER

#out.path <- here::here('output', 'glasgow_scaled/')
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

# Tran

```{r}

```

>>>>

#out.path <- here::here('output', 'glasgow_scaled/')
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

trans.path <- here::here('data', 'transitions/')
```

# PCS Pathways

1.  Housing Quality
2.  Nutrition Quality
3.  Tobacco Use
4.  Loneliness
5.  Physical Activity (new)
6.  Alcohol Use Disorders (new)

## Transition Model

The formula we use for estimating a transition model for PCS is shown below:

> SF_12_PCS ~ scale(SF_12_PCS_last) + I(scale(SF_12_PCS_last)\*\*2) + factor(sex) + relevel(factor(ethnicity), ref = 'WBI') + scale(age) + I(scale(age)\*\*2) + relevel(factor(region), ref = 'Scotland') + relevel(factor(education_state), ref = "1") + factor(housing_quality) + scale(hh_income) + scale(nutrition_quality) + I(factor(ncigs>0)) + factor(loneliness) + factor(active) + factor(auditc) + (1|pidp) + time

This can be grouped into categories: - Previous values - Demographics - Pathways - Random term

We use a Linear Mixed-effects Model (LMM) to calculate transition probabilities

```{r}
pcs.mod <- readRDS(file = paste0(trans.path, 'SF_12_PCS/lmm/SF_12_PCS_LMM.rds'))

summary(pcs.mod)
```
